---
title: "Comparing a novel bathing solution with standard care in terms of time to infection"
author: "Yeojoo Lee"
date: "2026-07-21"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(survival)
library(survminer)
library(ggplot2)
```

## Overview

This project applies survival analysis to compare a novel bathing solution with standard care in terms of time to infection among burn patients.

The analysis was completed as part of coursework in biostatistics and demonstrates my experience with R programming and survival analysis methods.

Data

The dataset used in this analysis was provided as part of coursework and is not included in this repository.

Statistical Methods

The primary outcome was time to infection, with infection status recorded as the event indicator.

The analysis includes:

Kaplan-Meier survival curves
Log-rank test
Comparison of time-to-infection between treatment groups
Analysis

The survival distribution was estimated using the Kaplan-Meier method and compared between the two treatment groups.

Results
Kaplan-Meier Survival Curves

```{r burn-km-plot}
# Load Dataset
burn <- read.csv("burn.csv")

# Define Bathing Solution factor labels
burn$bathsol_factor <- factor(burn$bathsol, levels = c(0, 1), labels = c("Control/Standard", "New Bathing Sol"))

# Fit Kaplan-Meier Curve
km_fit <- survfit(Surv(infecttime, infectevent) ~ bathsol_factor, data = burn)

# Visualize with survminer
ggsurvplot(
  km_fit,
  data = burn,
  pval = TRUE,
  conf.int = TRUE,
  risk.table = TRUE,
  legend.title = "Treatment Group",
  legend.labs = c("Control/Standard", "New Bathing Sol"),
  palette = c("#E41A1C", "#377EB8"),
  title = "Kaplan-Meier Time-to-Infection Estimates",
  xlab = "Time (Days)",
  ylab = "Infection-Free Probability"
)
```


